Two applications of logic programming to Coq

### 2021-03-05 papers/types2020/revisions/main.tex
starting a revision dir for types20. Initial work on sec 3
cleanup of the code directoty under types2020
Improved the abstract.

\documentclass[a4paper,USenglish,cleveref, autoref, thm-restate]{lipics-v2019}
\input head
\input preamble

\title{Two applications of logic programming to Coq} % Other suggestions?
% bit too general -- elpi-coq is such an interface -a,
% on the usefulness of logic programming in Coq
% two applications of logic programming to Coq
\titlerunning{Two applications of logic programming to Coq}

@@

\begin{abstract}
The \emph{foundational proof certificate} (FPC) framework is capable
of checking and elaborating a wide range of proof evidence and can easily
be implemented using the logic programming language \lP.
We use the recently released Coq-Elpi plugin for Coq in which the Elpi
implementation of \lP can send and retrieve information to and from the Coq kernel.
We provide two examples: first we implement a FPC-driven sequent calculus for a fragment of the Calculus of Inductive Constructions and we package it into a tactic to perform property-based testing of Inductive types corresponding to pure (higher-order) Horn programs. Secondly, we implement a proof checker for first-order LJF to demonstrate how  proof certificates
can be supplied by external (to Coq) provers and elaborated into the
fully detailed proof terms that can be checked by the Coq kernel.
\end{abstract}

@@

\input conc
\bibliography{l}
%\newpage
\appendix
\input app
\end{document}

@@

% LocalWords:  pbt elab conc Elpi LJF

>>>>

\documentclass[a4paper,USenglish,cleveref, autoref, thm-restate]{lipics-v2019}

\input{../head}
\input preamble

\title{Two applications of logic programming to Coq} 
\titlerunning{Two applications of logic programming to Coq}

@@

\begin{abstract}
The logic programming paradigm provides a flexible setting for
representing, manipulating, checking, and elaborating proof
structures.  This is particularly true when the logic programming
language allows for bindings in terms and proofs.  In this paper,
we make use of two recent innovations at the intersection of logic
programming and proof checking.  One of these is the
\emph{foundational proof certificate} (FPC) framework which provides a
flexible means of defining the semantics of a range of proof
structures for classical and intuitionistic logic.  A second
innovation is the recently released Coq-Elpi plugin for Coq in which
the Elpi implementation of \lP can send and retrieve information to
and from the Coq kernel.  We illustrate the use of both this Coq
plugin and FPCs with two example applications.  First, we implement an
FPC-driven sequent calculus for a fragment of the Calculus of
Inductive Constructions and we package it into a tactic to perform
property-based testing of inductive types corresponding to pure
(higher-order) Horn programs.  Second, we implement in Elpi a proof
checker for first-order intuitionistic logic and demonstrate how proof
certificates can be supplied by external (to Coq) provers and then
elaborated into the fully detailed proof terms that can be checked by
the Coq kernel.
\end{abstract}

@@

\input conc
\bibliography{../l}
%\newpage
\appendix
\input app
\end{document}

@@

% LocalWords:  pbt elab conc Elpi LJF FPC Coq sequent provers
